### 2021-06-30 src/paper/model/matching.tex
Restructure for arxiv submission.
Remove all comments by hand for arxiv.
Nicely format names. Add rapid test identifier to rapid test parameters.

The empirical data described above only allows to estimate the number of contacts each
person has. In order to simulate transmissions of Covid-19, the numbers of contacts has
to be translated into actual meetings between people. This is achieved by a matching
algorithm:

@@

Recurrent contacts are described by two components: 1) A set of time invariant groups, such as school classes. The groups can be sampled from empirical data or created by
randomly matching simulated individuals into groups. 2) A deterministic or random function that takes the value 0 (non-participating) and 1
(participating) and can depend on the weekday, date and health state. This can be used
to model vacations, weekends or symptomatic people who stay home (see section
\ref{sec:endogenous_contact_reductions} for details).

@@

The algorithm works as follows: First we randomly draw a contact type and individual.
For each contact of the drawn contact type that person has, we first draw the group of
the other person (first stage).
Next, we calculate the probability to be drawn for each member of the group, based on
the number of remaining contacts, i.e. people who have more remaining contacts are drawn
with a higher probability. The probabilities have to be re-calculated each time because
with each
matched contact, the number of remaining contacts changes. We then draw the other
individual, determine whether an infection takes place and if so update the health state
of the newly infected person. Finally, we reduce the number of remaining contacts of the
two matched individuals by one.\comment[id=J]{Add formulae here.}

>>>>

The empirical data described above only allows to estimate the number of contacts each
person has. In order to simulate transmissions of Covid-19, the numbers of contacts has
to be translated into actual meetings between people. This is achieved by a matching
algorithm:\comment[id=K]{comment from HM: Describe what happens if matching is not
perfect (i.e. if some people remain)}

@@

Recurrent contacts are described by two components: 1) A set of time invariant groups, such as school classes. The groups can be sampled from empirical data or created by
randomly matching simulated individuals into groups. 2) A deterministic or random function that takes the value 0 (non-participating) and 1
(participating) and can depend on the weekday, date and health state. This can be used
to model vacations, weekends or symptomatic people who stay home (see section
\ref{sec:policies} for details).

@@

The algorithm works as follows: First we randomly draw a contact type and individual.
For each contact of the drawn contact type that person has, we first draw the group of
the other person (first stage).
Next, we calculate the probability to be drawn for each member of the group, based on
the number of remaining contacts, i.e. people who have more remaining contacts are drawn
with a higher probability. The probabilities have to be re-calculated each time because
with each
matched contact, the number of remaining contacts changes. We then draw the other
individual, determine whether an infection takes place and if so update the health state
of the newly infected person. Finally, we reduce the number of remaining contacts of the
two matched individuals by one. \comment[id=J]{Add formulae here.}
